% Created 2016-03-07 Mon 22:38
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Balaji C}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Balaji C},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 24.5.1 (Org mode 8.3.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{2016-03-02}
\label{sec:orgheadline7}
\subsection{Planned}
\label{sec:orgheadline5}
\subsubsection{Start studying chapter 04 of real world haskell}
\label{sec:orgheadline1}
\subsubsection{Learn go use erc irc chat client in emacs}
\label{sec:orgheadline2}
\subsubsection{Implement merge sort in haskell using recursion}
\label{sec:orgheadline3}
\subsubsection{Implement simple graycode generator in haskell}
\label{sec:orgheadline4}
\subsection{NYSE\_CCG}
\label{sec:orgheadline6}
\section{2016-03-01}
\label{sec:orgheadline12}
\subsection{Planned}
\label{sec:orgheadline11}
\subsubsection{Complete chanpter 03 of real world haskell from safari}
\label{sec:orgheadline8}
\subsubsection{Enable org mode layer, for better bindings}
\label{sec:orgheadline9}
\subsubsection{Evil mode tutor for few minutes to improve keboard handling in evil mode}
\label{sec:orgheadline10}
\section{2016-02-29}
\label{sec:orgheadline18}
\subsection{Studied real world haskell chapter 03}
\label{sec:orgheadline13}
Finished till algebraic data types. Learned difference between value and type constuctor.
Coded some Bookstore examples in the ch03 directory.
Completed Recursive types and implemented list and tree data structure
\subsection{Integrated some trunk level repo changes in bitbucket}
\label{sec:orgheadline14}
Made trunk as the highlest level in repository. Created subfolders based on languages.
\subsection{Updated spacemacs config for C++, python and haskell}
\label{sec:orgheadline15}
Enabled layers for C++, python and haskell. Changed the hindent style to gibiansky
for comfortability in reading
\subsection{Installed below packages using cabal}
\label{sec:orgheadline17}
\subsubsection{hindent}
\label{sec:orgheadline16}
Default package was not installed. As a result hindent was not working with gibiansky
style code.
\end{document}
